Measuring the Type Ia supernova delay time distribution via host galaxy rates in the Dark Energy Survey

### 2021-01-19 draft.tex
Updates from Overleaf

\section{Linear fits using Hamiltonian Monte Carlo}
In this section we describe the procedures used to fit slopes and intercepts to the relationships measured in the analysis.

\label{appendix:linear_fits}
We model the relation with the linear relationship: 
\begin{equation}
    R_{\mathrm{G}} = \frac{\mathrm{d}R}{\mathrm{d}M_*} M_* + c \,,
\label{eq:rate_fit}
\end{equation}
where $dR/dM_*$ signifies the change of the rate of SNe as a function of the stellar mass, $c$ is a constant that sets the normalisation of the rate. We fit the model assuming a normal likelihood, such that the observed rate in each stellar mass bin is itself modelled as a Gaussian distribution described by the mean and standard deviation of the data in that bin. We adopt weakly informative normal priors on the slope and intercept: $p\left(\frac{\mathrm{d}R}{\mathrm{d}M_*}\right) \sim \mathcal{N}\left(0,5\right)$ and  $p\left(c\right) \sim \mathcal{N}\left(-12,5\right)$ respectively. We sample using 4 chains, each with 2000 warm up and 2000 sampling iterations. We report parameter estimates based on the mean and standard deviation of their posterior samples.

>>>>

\section{Linear fits using Bayesian inference}
In this section we describe the procedures used to fit slopes and intercepts to the relationships measured in the analysis.

\label{appendix:linear_fits}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/fit_fine_BC03_corner.png}
    \caption{Joint posterior distribution for the slope and intercept of the linear fit to the SN rate per galaxy per year as a function of stellar mass (Section \ref{sec:rates}; Fig. \ref{fig:rate_fitted}).}
    \label{fig:corner_slope_int}
\end{figure}
We model the relation with the linear relationship: 
\begin{equation}
    R_{\mathrm{G}} = \frac{\mathrm{d}R}{\mathrm{d}M_*} M_* + c \,,
\label{eq:rate_fit}
\end{equation}
where $dR/dM_*$ signifies the change of the rate of SNe as a function of the stellar mass, $c$ is a constant that sets the normalisation of the rate. We fit the model assuming a normal likelihood, such that the observed rate in each stellar mass bin is itself modelled as a Gaussian distribution described by the mean and standard deviation of the data in that bin. We adopt weakly informative normal priors on the slope and intercept: $p\left(\frac{\mathrm{d}R}{\mathrm{d}M_*}\right) \sim \mathcal{N}\left(0,5\right)$ and  $p\left(c\right) \sim \mathcal{N}\left(-12,5\right)$ respectively. We sample using 4 chains, each with 2000 warm up and 2000 sampling iterations. We report parameter estimates based on the mean and standard deviation of their posterior samples.
